An Audio-Based 3D Spatial Guidance AR System for Blind Users

### 2020-05-28 Manuscript.tex
Init

---
title: "An Audio-Based 3D Spatial Guidance AR System for Blind Users"
titlerunning: Audio-Based 3D Spatial Guidance
authorrunning: J. Couhlan et al.
output:
  pdf_document:
    template: res/templates/markdown.tex
    toc: no
    keep_tex: yes
institutes:
- id: 1
  name: The Smith-Kettlewell Eye Research Institute, San Francisco, CA
  emails: coughlan@ski.org, brandon.biggs@ski.org, hshen@ski.org
- id: 2
  name: LITIS, University of Rouen, Normandy, France
  emails: marc-aurele.riviere@univ-rouen.fr
keywords:
- Assisitive Devices
- Augmented Reality
- Auditory Substitution
- Visual Impairment
abstract: Augmented reality (AR) has great potential for blind users because it enables
  a range of applications that provide audio information about specific locations
  or directions in the user’s environment. For instance, the CamIO (“Camera Input-Output”)
  AR app makes physical objects (such as documents, maps, devices and 3D models) accessible
  to blind and visually impaired persons by providing real-time audio feedback in
  response to the location on an object that the user is touching (using an inexpensive
  stylus). An important feature needed by blind users of AR apps such as CamIO is
  a 3D spatial guidance feature that provides real-time audio feedback to help the
  user find a desired location on an object. We have devised a simple audio interface
  to provide verbal guidance towards a target of interest in 3D. The experiment we
  report with blind participants using this guidance interface demonstrates the feasibility
  of the approach and its benefit for helping users find locations of interest.
authors:
- name: James Coughlan
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Brandon Biggs
  orcid: 0000-1111-2222-3333
  inst: 1
- name: Marc-Aurèle Rivière
  orcid: 0000-0002-5108-3382
  inst: 2
- name: Huiying Shen
  orcid: 0000-1111-2222-3333
  inst: 1
ressources: res/
templates: res/templates/
bibliography: res/refs.bib
---

```{r setup, include=FALSE}

#TODO: DESCRIPTION with package metadata ?

knitr::opts_chunk$set(
  fig.show="hold",
  fig.align="default",
  warning = FALSE,
  echo = FALSE,
  cache = FALSE,
  error = FALSE
)

colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, x)
  } else x
}
```

# State of the Art and Related Technology {#sota}

@@

Audio labels are a powerful supplement or alternative to braille labels. Standard methods of implementing audio labels require the use of special hardware and materials, which is costly and limits their adoption. For instance, tactile graphics may be overlaid on a touch-sensitive tablet \cite{TalkingTactileTablet}. Documents or other surfaces can be covered with a special form of paper readable by a “smart pen” \cite{mieleTalkingTactileApps2010}. The PenFriend \cite{kendrickPenFriendTouchMemo2011} stylus uses small barcodes affixed to an object to define audio labels.

There is growing interest in using computer vision-based approaches for audio labeling. In these approaches a camera tracks the user’s fingers or handheld pointer as they explore an object, enabling audio labeling for existing objects with minimal or no customization. Past computer vision approaches to audio labeling include \cite{shiMarkitTalkitLowBarrier2017}, which focuses on 3D printed objects, \cite{thevinAugmentedRealityPeople2018}, which uses a depth camera to access flat documents, and \cite{fuscoTactileGraphicsHelper2015}, which provides access to tactile graphics to students in educational settings.

We build on our past work on CamIO \cite{shenCamIO3DComputer2013,coughlanEvaluatingAuthorUser2017,coughlanTowardsAccessibleAudioLabeling2020}, which is short for “Camera Input-Output.” We have implemented CamIO as a stand-alone iPhone app that tracks an inexpensive wooden stylus held by the user to point at locations of interest on an object (called hotspots). When the user points at a hotspot with the stylus tip, relevant audio information, such as text-to-speech or other sounds, is announced.

@@

# Overview of the CamIO System {#overview}

CamIO is an augmented reality (AR) iPhone app that uses computer vision to provide audio labels for rigid 3D objects. The rigid object of interest is mounted on a board, which is a printed barcode pattern (\ref{fig:exp}) that allows CamIO to estimate the object’s pose (3D translation and 3D orientation) relative to the camera. The iPhone is typically mounted on a tripod or a gooseneck cellphone holder \ref{fig:exp} to obtain a clear view of the board and object, but in some cases \cite{coughlanTowardsAccessibleAudioLabeling2020} users may hold the iPhone by hand. The user points the tip of a passive wooden stylus \ref{fig:exp}, covered with another barcode pattern, to different locations on an object. CamIO estimates the stylus tip’s 3D location relative to the camera and uses the pose estimate of the board to determine the stylus tip’s 3D location relative to the object. Whenever the tip is close enough to a pre-defined hotspot, it triggers audio information about the hotspot. (In other words, hotspot locations are defined relative to the board, which is mounted rigidly to the object.)

@@

# 3D Spatial Guidance Interface {#material}

@@

Informal tests with two blind participants (one female of age 42, who is also participant P1 in the experiment described in the next section, and one male of age 73) showed that this guidance worked satisfactorily in some cases. However, we found that the feedback was too indirect: the participants didn’t always know how to move the stylus to increase the tempo. As a result, the resulting guidance process was unacceptably slow.
Thus we devised a second, more direct guidance approach: verbal directions telling the user to move the stylus along the cardinal directions (up, down, left, right, forward or back). While the optimal direction to move the stylus tip towards the hotspot might entail a combination of these directions (e.g., simultaneously move left and up), for simplicity we issue directions along only one cardinal direction at a time – the direction that will most improve the alignment to the target.

We define the guidance interface as follows. The board (barcode pattern beneath the truck, see \ref{fig:exp}) defines an xyz coordinate frame, with $+x$ = right, $-x$ = left, $+y$ = forward (away from the user), $-y$ = back (towards the user), $+z$ = up and $-z$ = down. Let the desired target hotspot location be denoted $(x*, y*, z*)$, and the current location of the stylus tip be $(x,y,z)$. Define the error vector $e = (x-x*, y-y*, z-z*)$, and let index $a = argmax_i |e_i|$, i.e., a is the index (1, 2 or 3, corresponding to x, y or z, respectively) of the entry in e with the highest absolute value. In other words, a indicates which coordinate (x, y or z) is most discrepant from the target coordinate location $(x*, y*, z*)$. Then the appropriate direction is issued, e.g., “left” if $a = 1$ and $x > x*$, “right” if $a = 1$ and $x < x*$, “up” if $a = 3$ and $z < z*$, etc. Directions are announced roughly twice per second whenever the stylus is visible. The target hotspot is announced when the stylus gets to within approximately 1 cm from the hotspot. No audio feedback is issued when the stylus is not visible.

# Experiment with Blind Participants {#exp}

We conducted an experiment to assess the feasibility of the spatial guidance feedback and to determine whether the feedback speeds up the target search. The experiment \ref{fig:exp} compared how much time a blind participant needed to find hotspots (points of interest) on a 3D object with spatial guidance vs. without it. The object was a large toy fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations defined in advance. The hotspots were tactilely salient features such as lights, hooks or other features that protruded from the truck. Some hotspots were in recessed locations on the truck, such as the shift stick and steering wheel (\ref{fig:exp}) in the front cabin, or on the side of the truck facing away from the participant; these hotspots were difficult to find and access, whether by fingertip or by stylus. In fact, the difficulty of accessing such locations highlights an advantage of the CamIO stylus, whose tip need not be visible to the camera. This allows the user to explore recessed areas or areas that are otherwise invisible to the camera.

```{r exp, out.width=c("55%","45%"), fig.cap="(left) Blind participant uses CamIO to explore a toy fire truck. The participant holds the CamIO stylus (a barcode pattern printed on a square wooden dowel with a pointy tip) to point to possible hotspots on the truck. The truck is glued to the board, a piece of paper with a separate barcode pattern, which is taped to the table. An iPhone 8 running CamIO is held by a gooseneck cellphone holder to capture a view of the truck, board and stylus. (right) Stylus points to steering wheel in the truck cabin. Though the steering wheel is in a recessed location that is not visible to CamIO, the stylus tip location can still be estimated."}

knitr::include_graphics("res/img/fig1a.jpg")
knitr::include_graphics("res/img/fig1b.jpg")
```

Each hotspot location was searched for under two feedback conditions: G (guidance provided) and NG (no guidance). The participant was given up to 120 sec. to find each hotspot, after which a time-out was declared. In order to minimize the influence of any possible learning effects, which could make it easier to find a hotspot the second time it was searched for, we randomized the sequence of hotspots and alternated between NG and G trials. This resulted in a sequence of 2K = 20 trials, starting with an NG trial, the same sequence for each participant.

We had a total of N=4 blind participants in our experiment (2 male/2 female, ages from 26-42). Participants P1, P3 and P4 were already familiar with the CamIO system (P4 is a co-author of this paper) while P2 was unfamiliar with it. None of the participants was told the study design before their trials, and we didn’t tell them whether or not any locations would be repeated in the 20 trials. After obtaining IRB consent, we reviewed how CamIO works if necessary and demonstrated the audio guidance feature. The experimenter launched CamIO on an iPhone 8 and positioned it on a gooseneck cellphone holder so that the camera captured the entire truck and board.
Each participant spent a short time practicing with the guidance feature, with help provided by the experimenter as needed. (The experimenter chose practice hotspots that were different from the pre-defined K=10 hotspots.) In the practice phase, the experimenter explained that barriers sometimes block the user from moving in the suggested guidance direction. For instance, if in \ref{fig:exp} the system directs the participant to move “forward” towards the left side mirror, the stylus will soon hit the cabin roof/wall as it moves towards the mirror; the participant must find ways around such obstacles to find the target hotspot.

@@

# Experimental Results and Analysis {#results}

We conducted an experiment to assess the feasibility of the spatial guidance feedback and to determine whether the feedback speeds up the target search. The experiment (\ref{fig:exp}) compared how much time a blind participant needed to find hotspots (points of interest) on a 3D object with spatial guidance vs. without it. The object was a large toy fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations defined in advance. The hotspots were tactilely salient features such as lights, hooks or other features that protruded from the truck. Some hotspots were in recessed locations on the truck, such as the shift stick and steering wheel (\ref{fig:exp}) in the front cabin, or on the side of the truck facing away from the participant; these hotspots were difficult to find and access, whether by fingertip or by stylus. In fact, the difficulty of accessing such locations highlights an advantage of the CamIO stylus, whose tip need not be visible to the camera. This allows the user to explore recessed areas or areas that are otherwise invisible to the camera.

@@

We analyzed the differences between times under G vs. NG using a Wilcoxon signed rank test. The resulting p-value is p = 3.8 x 10-8. This is a highly statistically significant p-value supporting the rejection of the null hypothesis that the distribution of times under G is the same as the distribution of times under NG.

The following System Usability Scale (SUS) scores were calculated: P1=65, P2=75, P3=77.5, for an average of 72.5. An SUS score of 68 is considered “average” while scores in the mid- to high 70s are considered “good” (\url{https://measuringu.com/interpret-sus-score/}). Overall, the SUS scores suggest that the guidance system is usable but needs improvement.

@@

# Conclusion {#conclusion}

We have devised a 3D spatial guidance system that helps a blind user find a specific location of interest on an object using CamIO, an audio-based AR system. The guidance system uses simple verbal commands (“left”/ “right”/“up”/etc.) to tell the user which direction to move the stylus tip. Experiments with four blind participants show that the guidance system significantly speeds up the search for target hotspots compared with an exhaustive search. A secondary contribution of this study is to demonstrate the ability of the CamIO stylus to access recessed or otherwise obscured locations on an object that are not themselves visible to the camera.

While we applied this guidance approach specifically to CamIO, it could be useful in any AR system, whether the system tracks the user’s hands, handheld stylus or other pointing tool. Such audio-based guidance is not only helpful for blind users but is also useful in applications where visibility is limited (either by environmental conditions or because of a visual impairment), or for sighted users who prefer a cross-sensory display (e.g., audio and visual combined).

Future work will focus on refining and improving the audio interface. One possible way to speed up the guidance process is to add more specific directional feedback, e.g., “far left” would tell the user to move the stylus farther to the left than the “left” instruction. The verbal directions could be augmented with 3D spatialized sound as in \cite{mayAuditoryDisplaysFacilitate2019}, which could make the guidance more intuitive. Finally, we will continue to test and improve the CamIO system, with an emphasis on refining the spatial accuracy of the tip location estimates using improved computer vision algorithms.

>>>>

% This is template.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04

\documentclass[runningheads]{res/templates/llncs}

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{etoolbox}

% Include packages from YAML header

\begin{document}

\title{An Audio-Based 3D Spatial Guidance AR System for Blind Users}

\titlerunning{Audio-Based 3D Spatial Guidance}
%
\newbool{flag}
\boolfalse{flag}
%
\author{
\ifbool{flag}{\and}{\booltrue{flag}}James Coughlan\inst{1}\orcidID{0000-1111-2222-3333}
\ifbool{flag}{\and}{\booltrue{flag}}Brandon Biggs\inst{1}\orcidID{0000-1111-2222-3333}
\ifbool{flag}{\and}{\booltrue{flag}}Marc-Aurèle Rivière\inst{2}\orcidID{0000-0002-5108-3382}
\ifbool{flag}{\and}{\booltrue{flag}}Huiying Shen\inst{1}\orcidID{0000-1111-2222-3333}
}
%
\authorrunning{J. Couhlan et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\boolfalse{flag}
%
\institute{
\ifbool{flag}{\and}{\booltrue{flag}}
 The Smith-Kettlewell Eye Research Institute, San Francisco, CA \\
 \email{\href{mailto:coughlan@ski.org}{\nolinkurl{coughlan@ski.org}},
\href{mailto:brandon.biggs@ski.org}{\nolinkurl{brandon.biggs@ski.org}},
\href{mailto:hshen@ski.org}{\nolinkurl{hshen@ski.org}}} 
\ifbool{flag}{\and}{\booltrue{flag}}
 LITIS, University of Rouen, Normandy, France \\
 \email{\href{mailto:marc-aurele.riviere@univ-rouen.fr}{\nolinkurl{marc-aurele.riviere@univ-rouen.fr}}} 
}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Augmented reality (AR) has great potential for blind users because it
enables a range of applications that provide audio information about
specific locations or directions in the user's environment. For
instance, the CamIO (``Camera Input-Output'') AR app makes physical
objects (such as documents, maps, devices and 3D models) accessible to
blind and visually impaired persons by providing real-time audio
feedback in response to the location on an object that the user is
touching (using an inexpensive stylus). An important feature needed by
blind users of AR apps such as CamIO is a 3D spatial guidance feature
that provides real-time audio feedback to help the user find a desired
location on an object. We have devised a simple audio interface to
provide verbal guidance towards a target of interest in 3D. The
experiment we report with blind participants using this guidance
interface demonstrates the feasibility of the approach and its benefit
for helping users find locations of interest.
\\
\boolfalse{flag}
\keywords{
\ifbool{flag}{\and}{\booltrue{flag}}
Assisitive Devices
\ifbool{flag}{\and}{\booltrue{flag}}
Augmented Reality
\ifbool{flag}{\and}{\booltrue{flag}}
Auditory Substitution
\ifbool{flag}{\and}{\booltrue{flag}}
Visual Impairment
}
\end{abstract}
%
%
\hypertarget{sota}{%
\section{State of the Art and Related Technology}\label{sota}}

@@

Audio labels are a powerful supplement or alternative to braille labels.
Standard methods of implementing audio labels require the use of special
hardware and materials, which is costly and limits their adoption. For
instance, tactile graphics may be overlaid on a touch-sensitive tablet
\cite{TalkingTactileTablet}. Documents or other surfaces can be covered
with a special form of paper readable by a ``smart pen''
\cite{mieleTalkingTactileApps2010}. The PenFriend
\cite{kendrickPenFriendTouchMemo2011} stylus uses small barcodes affixed
to an object to define audio labels.

There is growing interest in using computer vision-based approaches for
audio labeling. In these approaches a camera tracks the user's fingers
or handheld pointer as they explore an object, enabling audio labeling
for existing objects with minimal or no customization. Past computer
vision approaches to audio labeling include
\cite{shiMarkitTalkitLowBarrier2017}, which focuses on 3D printed
objects, \cite{thevinAugmentedRealityPeople2018}, which uses a depth
camera to access flat documents, and
\cite{fuscoTactileGraphicsHelper2015}, which provides access to tactile
graphics to students in educational settings.

We build on our past work on CamIO
\cite{shenCamIO3DComputer2013,coughlanEvaluatingAuthorUser2017,coughlanTowardsAccessibleAudioLabeling2020},
which is short for ``Camera Input-Output.'' We have implemented CamIO as
a stand-alone iPhone app that tracks an inexpensive wooden stylus held
by the user to point at locations of interest on an object (called
hotspots). When the user points at a hotspot with the stylus tip,
relevant audio information, such as text-to-speech or other sounds, is
announced.

@@

\hypertarget{overview}{%
\section{Overview of the CamIO System}\label{overview}}

CamIO is an augmented reality (AR) iPhone app that uses computer vision
to provide audio labels for rigid 3D objects. The rigid object of
interest is mounted on a board, which is a printed barcode pattern
(\ref{fig:exp}) that allows CamIO to estimate the object's pose (3D
translation and 3D orientation) relative to the camera. The iPhone is
typically mounted on a tripod or a gooseneck cellphone holder
\ref{fig:exp} to obtain a clear view of the board and object, but in
some cases \cite{coughlanTowardsAccessibleAudioLabeling2020} users may
hold the iPhone by hand. The user points the tip of a passive wooden
stylus \ref{fig:exp}, covered with another barcode pattern, to different
locations on an object. CamIO estimates the stylus tip's 3D location
relative to the camera and uses the pose estimate of the board to
determine the stylus tip's 3D location relative to the object. Whenever
the tip is close enough to a pre-defined hotspot, it triggers audio
information about the hotspot. (In other words, hotspot locations are
defined relative to the board, which is mounted rigidly to the object.)

@@

\hypertarget{material}{%
\section{3D Spatial Guidance Interface}\label{material}}

@@

Informal tests with two blind participants (one female of age 42, who is
also participant P1 in the experiment described in the next section, and
one male of age 73) showed that this guidance worked satisfactorily in
some cases. However, we found that the feedback was too indirect: the
participants didn't always know how to move the stylus to increase the
tempo. As a result, the resulting guidance process was unacceptably
slow. Thus we devised a second, more direct guidance approach: verbal
directions telling the user to move the stylus along the cardinal
directions (up, down, left, right, forward or back). While the optimal
direction to move the stylus tip towards the hotspot might entail a
combination of these directions (e.g., simultaneously move left and up),
for simplicity we issue directions along only one cardinal direction at
a time -- the direction that will most improve the alignment to the
target.

We define the guidance interface as follows. The board (barcode pattern
beneath the truck, see \ref{fig:exp}) defines an xyz coordinate frame,
with \(+x\) = right, \(-x\) = left, \(+y\) = forward (away from the
user), \(-y\) = back (towards the user), \(+z\) = up and \(-z\) = down.
Let the desired target hotspot location be denoted \((x*, y*, z*)\), and
the current location of the stylus tip be \((x,y,z)\). Define the error
vector \(e = (x-x*, y-y*, z-z*)\), and let index \(a = argmax_i |e_i|\),
i.e., a is the index (1, 2 or 3, corresponding to x, y or z,
respectively) of the entry in e with the highest absolute value. In
other words, a indicates which coordinate (x, y or z) is most discrepant
from the target coordinate location \((x*, y*, z*)\). Then the
appropriate direction is issued, e.g., ``left'' if \(a = 1\) and
\(x > x*\), ``right'' if \(a = 1\) and \(x < x*\), ``up'' if \(a = 3\)
and \(z < z*\), etc. Directions are announced roughly twice per second
whenever the stylus is visible. The target hotspot is announced when the
stylus gets to within approximately 1 cm from the hotspot. No audio
feedback is issued when the stylus is not visible.

\hypertarget{exp}{%
\section{Experiment with Blind Participants}\label{exp}}

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment \ref{fig:exp} compared how much time a
blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (\ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

\begin{figure}
\includegraphics[width=0.55\linewidth]{res/img/fig1a} \includegraphics[width=0.45\linewidth]{res/img/fig1b} \caption{(left) Blind participant uses CamIO to explore a toy fire truck. The participant holds the CamIO stylus (a barcode pattern printed on a square wooden dowel with a pointy tip) to point to possible hotspots on the truck. The truck is glued to the board, a piece of paper with a separate barcode pattern, which is taped to the table. An iPhone 8 running CamIO is held by a gooseneck cellphone holder to capture a view of the truck, board and stylus. (right) Stylus points to steering wheel in the truck cabin. Though the steering wheel is in a recessed location that is not visible to CamIO, the stylus tip location can still be estimated.}\label{fig:exp}
\end{figure}

Each hotspot location was searched for under two feedback conditions: G
(guidance provided) and NG (no guidance). The participant was given up
to 120 sec.~to find each hotspot, after which a time-out was declared.
In order to minimize the influence of any possible learning effects,
which could make it easier to find a hotspot the second time it was
searched for, we randomized the sequence of hotspots and alternated
between NG and G trials. This resulted in a sequence of 2K = 20 trials,
starting with an NG trial, the same sequence for each participant.

We had a total of N=4 blind participants in our experiment (2 male/2
female, ages from 26-42). Participants P1, P3 and P4 were already
familiar with the CamIO system (P4 is a co-author of this paper) while
P2 was unfamiliar with it. None of the participants was told the study
design before their trials, and we didn't tell them whether or not any
locations would be repeated in the 20 trials. After obtaining IRB
consent, we reviewed how CamIO works if necessary and demonstrated the
audio guidance feature. The experimenter launched CamIO on an iPhone 8
and positioned it on a gooseneck cellphone holder so that the camera
captured the entire truck and board. Each participant spent a short time
practicing with the guidance feature, with help provided by the
experimenter as needed. (The experimenter chose practice hotspots that
were different from the pre-defined K=10 hotspots.) In the practice
phase, the experimenter explained that barriers sometimes block the user
from moving in the suggested guidance direction. For instance, if in
\ref{fig:exp} the system directs the participant to move ``forward''
towards the left side mirror, the stylus will soon hit the cabin
roof/wall as it moves towards the mirror; the participant must find ways
around such obstacles to find the target hotspot.

@@

\hypertarget{results}{%
\section{Experimental Results and Analysis}\label{results}}

We conducted an experiment to assess the feasibility of the spatial
guidance feedback and to determine whether the feedback speeds up the
target search. The experiment (\ref{fig:exp}) compared how much time a
blind participant needed to find hotspots (points of interest) on a 3D
object with spatial guidance vs.~without it. The object was a large toy
fire truck (27 cm x 12 cm x 14 cm), with K=10 distinct hotspot locations
defined in advance. The hotspots were tactilely salient features such as
lights, hooks or other features that protruded from the truck. Some
hotspots were in recessed locations on the truck, such as the shift
stick and steering wheel (\ref{fig:exp}) in the front cabin, or on the
side of the truck facing away from the participant; these hotspots were
difficult to find and access, whether by fingertip or by stylus. In
fact, the difficulty of accessing such locations highlights an advantage
of the CamIO stylus, whose tip need not be visible to the camera. This
allows the user to explore recessed areas or areas that are otherwise
invisible to the camera.

@@

We analyzed the differences between times under G vs.~NG using a
Wilcoxon signed rank test. The resulting p-value is p = 3.8 x 10-8. This
is a highly statistically significant p-value supporting the rejection
of the null hypothesis that the distribution of times under G is the
same as the distribution of times under NG.

The following System Usability Scale (SUS) scores were calculated:
P1=65, P2=75, P3=77.5, for an average of 72.5. An SUS score of 68 is
considered ``average'' while scores in the mid- to high 70s are
considered ``good'' (\url{https://measuringu.com/interpret-sus-score/}).
Overall, the SUS scores suggest that the guidance system is usable but
needs improvement.

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

We have devised a 3D spatial guidance system that helps a blind user
find a specific location of interest on an object using CamIO, an
audio-based AR system. The guidance system uses simple verbal commands
(``left''/ ``right''/``up''/etc.) to tell the user which direction to
move the stylus tip. Experiments with four blind participants show that
the guidance system significantly speeds up the search for target
hotspots compared with an exhaustive search. A secondary contribution of
this study is to demonstrate the ability of the CamIO stylus to access
recessed or otherwise obscured locations on an object that are not
themselves visible to the camera.

While we applied this guidance approach specifically to CamIO, it could
be useful in any AR system, whether the system tracks the user's hands,
handheld stylus or other pointing tool. Such audio-based guidance is not
only helpful for blind users but is also useful in applications where
visibility is limited (either by environmental conditions or because of
a visual impairment), or for sighted users who prefer a cross-sensory
display (e.g., audio and visual combined).

Future work will focus on refining and improving the audio interface.
One possible way to speed up the guidance process is to add more
specific directional feedback, e.g., ``far left'' would tell the user to
move the stylus farther to the left than the ``left'' instruction. The
verbal directions could be augmented with 3D spatialized sound as in
\cite{mayAuditoryDisplaysFacilitate2019}, which could make the guidance
more intuitive. Finally, we will continue to test and improve the CamIO
system, with an emphasis on refining the spatial accuracy of the tip
location estimates using improved computer vision algorithms.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{res/templates/splncs04}
% \bibliography{bibliography}
\bibliography{res/refs.bib}

\end{document}
